---
title: "p8105_hw1_yy3662"
author: "Yunyi Yang"
date: "2025-09-17"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(tidyverse)
library(moderndive)
library(skimr)
data("early_january_weather")
skimr::skim(early_january_weather)

```

Thsi data set includes `origin`, which means waether station, `year` `month` `day` `hour` means time of recording, `temp` `dewp` means temperature and dewpoint in F, `humid` means relative humidity, `wind_dir` `wind_speed` `wind_gust` means wind direction (in degrees)m speed and gust speed (in mph), `precip` means precipitation, in inches, `pressure` means sea level pressure in millibars, `visib` means visibility in miles, `time_hour` means date and hour of the recording as a POSIXct date.

The data is 358*15.

The mean temperature is 39.58212 based on mean(early_january_weather$temp).

```{r}
library(ggplot2)
ggplot(data = early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("plot.png")
```

This plot has obvious rise and fall as the changing of time. At the same time, the higher humid level always happens in increasing process.

## Problem 2

```{r}
col1 <- rnorm(10)
col2 <- as.logical(col1 > 0)
col3 <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j")
col4 <- factor(c("1", "2", "3", "3", "2", "1", "1", "2", "3", "3"))
dataframe <- tibble(
  col1,
  col2,
  col3,
  col4
)
dataframe
mean(pull(dataframe, 1))
mean(pull(dataframe, 2))
mean(pull(dataframe, 3))
mean(pull(dataframe, 4))
newcol2 <- as.numeric(col2)
newcol3 <- as.numeric(col3)
newcol4 <- as.numeric(col4)
```
For mean, it works for samples from N(0,1) and logical variable, and it doesn't work for character vectors and factor vectors.
After I doing as.numeric, these three columns become numeric data, and the values of character vectors become NA in new numeric data because character vectors could contain letters and other format of data, not only including numeric numbers, so it doesn't make sense to convert character vector to numeric data. It is helpful for explaining the NA outcome when I do the mean for character vector because the informations that the character vector contain is not reasonable for mean function.