---
title: "p8105_hw1_yy3662"
author: "Yunyi Yang"
date: "2025-09-17"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(tidyverse)
library(moderndive)
library(skimr)
data("early_january_weather")
skimr::skim(early_january_weather)

```

Thsi data set includes `origin`, which means waether station, `year` `month` `day` `hour` means time of recording, `temp` `dewp` means temperature and dewpoint in F, `humid` means relative humidity, `wind_dir` `wind_speed` `wind_gust` means wind direction (in degrees)m speed and gust speed (in mph), `precip` means precipitation, in inches, `pressure` means sea level pressure in millibars, `visib` means visibility in miles, `time_hour` means date and hour of the recording as a POSIXct date.

The data is 358*15.

The mean temperature is 39.58212 based on mean(early_january_weather$temp).

```{r}
library(ggplot2)
ggplot(data = early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("plot.png")
```

This plot has obvious rise and fall as the changing of time. At the same time, the higher humid level always happens in increasing process.